BERT Model Compression and Weight Sharing

### 2019-05-11 paper/paper.tex
Add background in paper

\section{Background}
Example Structure:
\begin{itemize}
\item What information does a non-expert need to know about the problem domain?
\item What data exists for this problem?
\item What are the challenges/opportunities inherent to the data? (High dimensional, sparse, missing data, noise, structure, discrete/continuous, etc?)
\end{itemize}

>>>>

\section{Background}
Deep Neurel Networks (DNNs) have become extremely large in size with growing complexities. A BERT base model has 110M parameters and takes 438 MB disk space to store. This makes it very hard to deploy those models on mobile devices, which in most cases have limited storage and RAM and lower computational resources. The challenge that we are facing is how to compress DNNs in size while keeping their predictive performance competitive with full model.

% Example Structure:
% \begin{itemize}
% \item What information does a non-expert need to know about the problem domain?
% \item What data exists for this problem?
% \item What are the challenges/opportunities inherent to the data? (High dimensional, sparse, missing data, noise, structure, discrete/continuous, etc?)
% \end{itemize}
